### 2018-07-06 paper/5-implementations.tex
Rename build to fetch in suspending

\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- Shake build system; stores verifying traces
shake :: (Ord k, Hashable v) => Build Monad (VT k v) k v
shake = suspending vtRebuilder
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A task rebuilder based on verifying traces
vtRebuilder :: (Eq k, Hashable v) => Rebuilder Monad (VT k v) k v
vtRebuilder key value task = Task $ \fetch -> do
    upToDate <- verifyVT key (hash value) (fmap hash . fetch) =<< get
    if upToDate then return value else do
        (newValue, deps) <- track task fetch
        modify $ recordVT key (hash newValue) [ (k, hash v) | (k, v) <- deps ]
        return newValue
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A suspending task scheduler
suspending :: Ord k => Scheduler Monad i i k v
suspending rebuilder tasks target store = fst $ execState (build target) (store, Set.empty)
  where
    build :: k -> State (Store i k v, Set k) v
    build key = do
        done <- gets snd
        case tasks key of
            Just task | key `Set.notMember` done -> do
                value <- gets (getValue key . fst)
                let newTask :: Task (MonadState i) k v
                    newTask = rebuilder key value task
                newValue <- liftRun newTask build
                modify $ \(s, d) -> (updateValue key value newValue s, Set.insert key d)
                return newValue
            _ -> gets (getValue key . fst) -- fetch the existing value
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- Run a Task using Store to obtain the i
liftRun :: Task (MonadState i) k v
        -> (k -> State (Store i k v, Set k) v) -> State (Store i k v, Set k) v
\end{minted}
\vspace{-3mm}
\caption{An implementation of \Shake using our framework.}\label{fig-shake-implementation}
\vspace{-6mm}
\end{figure}

>>>>

\begin{figure}
\begin{minted}[fontsize=\small]{haskell}
-- Shake build system; stores verifying traces
shake :: (Ord k, Hashable v) => Build Monad (VT k v) k v
shake = suspending vtRebuilder
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A task rebuilder based on verifying traces
vtRebuilder :: (Eq k, Hashable v) => Rebuilder Monad (VT k v) k v
vtRebuilder key value task = Task $ \fetch -> do
    upToDate <- verifyVT key (hash value) (fmap hash . fetch) =<< get
    if upToDate then return value else do
        (newValue, deps) <- track task fetch
        modify $ recordVT key (hash newValue) [ (k, hash v) | (k, v) <- deps ]
        return newValue
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- A suspending task scheduler
suspending :: Ord k => Scheduler Monad i i k v
suspending rebuilder tasks target store = fst $ execState (fetch target) (store, Set.empty)
  where
    fetch :: k -> State (Store i k v, Set k) v
    fetch key = do
        done <- gets snd
        case tasks key of
            Just task | key `Set.notMember` done -> do
                value <- gets (getValue key . fst)
                let newTask :: Task (MonadState i) k v
                    newTask = rebuilder key value task
                newValue <- liftRun newTask fetch
                modify $ \(s, d) -> (updateValue key value newValue s, Set.insert key d)
                return newValue
            _ -> gets (getValue key . fst) -- fetch the existing value
\end{minted}
\vspace{0mm}
\begin{minted}[fontsize=\small]{haskell}
-- Run a Task using Store to obtain the i
liftRun :: Task (MonadState i) k v
        -> (k -> State (Store i k v, Set k) v) -> State (Store i k v, Set k) v
\end{minted}
\vspace{-3mm}
\caption{An implementation of \Shake using our framework.}\label{fig-shake-implementation}
\vspace{-6mm}
\end{figure}
